Impact of engines scheduler on the performance of Big Data pipelines in HPC

### 2021-01-21 latex/paper.tex
Drafted the infrastructure part (partial)

\section{Methods}
\subsection{Infrastructure} % TODO

>>>>

\section{Methods}
\subsection{Infrastructure}
For our experiments we used the SlashBin cluster at Concordia University.
Each compute node has 2 16-cores CPUs,
\SI{256}{\giga\byte} memory, \MD{find out what's the memory speed and \#-channel supported.}
\SI{2.88}{\tera\byte} SSDs of mounted storage.
The nodes are interconnected with a dedicated \SI{10}{\giga\bit/\second} Ethernet connection.
Centos \MD{Verify version} and Linux kernel \MD{Verify kernel version} is installed on the nodes.

\MD{Write about the worker/leader setup once the dataset size is determined. Need to tune so that 2-3 blocks can fit in the excutors memmory}
